An IFS study of Low-powered Radio Galaxies

### 2018-09-18 paper.tex
Propergating alterations to thesis to paper
 On branch master
 Changes to be committed:
	modified:   KDC_size_age.png
	modified:   M_k_binned.png
	modified:   Mg_sigma.png
	modified:   lambda_R_ellipticity.png
	modified:   nuclear_MEx.png
	modified:   paper.tex
	modified:   produce_maps.py
	modified:   refs.bib

\usepackage[flushleft, referable]{threeparttablex} % Adding notes under tables
\usepackage{mhchem} 	% typeset chemistry symbols
\usepackage{array} % For wrapping text in cell in tables with multicolumntype

@@

In this paper, we present a complete sample of 11 nearby low-powered radio galaxies, observed with a suite of instruments. This paper focuses on the spatially-resolved stellar kinematics, stellar populations, and ionized gas distribution, kinematics and ionization derived from optical IFS observations, while other observation such as \ce{^{12}CO(2-1)} from Atacama Large Millimeter/sub-millimeter Array (ALMA) and radio continuum from the Very Large Array (VLA) will be presented in future papers, but are overlaid on our maps (cyan and red contours respectively, in Figs \ref{fig:eso443}-\ref{fig:pks718}). We compare the characteristics and properties of our sample to those of ordinary (i.e.\ optically-selected) ETGs using the Atlas$^\text{3D}$ and MASSIVE IFS surveys. These include the fast/slow rotator classification fraction, kinematic substructures, absorption line strength radial gradients, general stellar population properties, ionized gas distribution and kinematics and the dominant source of ionizing photons.

@@

\section{Introduction}
	\label{sec:intro}
	It is becoming increasingly clear that two different types of active galactic nuclei (AGN) exist, radiative and jet mode AGN \citep[e.g.][]{Antonucci2012, Heckman2014}, raising speculation about differing mechanisms and possibly fuel sources for each. The former is thought to be the powerful engine that initially and rapidly shuts off star formation in massive early-type galaxies (ETGs; e.g. \citealt{Thomas2005, Thomas2010}), either by removing the cold gas from the galaxy entirely, heating it such that it joins the hot X-ray gas often present in massive galaxies \citep[e.g.][]{OSullivan2001}, or rendering it unusable for star formation (such as by stabilising it against collapse; e.g.\ \citealt{Martig2009}). After a single radiative-mode episode, the AGN is thought to subside to become jet-dominated, repeatedly reheating the surrounding interstellar medium (ISM) to counter any cooling that might allow the cold gas reservoir to replenish (and subsequently form stars).

@@

	\begin{table*}
		\centering
	% \begin{threeparttable}
		\caption{Key characteristics of the Southern Sample galaxies. Col.\,1: host galaxy name. Col.\,2: radio source name from Parkes Southern Radio Source Catalogue. We hereafter refer to the last galaxy by its PKS name only. Col.\,3: redshift. Col.\,4: National Radio Astronomy Observatory (NRAO) VLA Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}. Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}). Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}.}
		\label{tab:sample}
		\begin{tabular}{l c c c c l}
			\hline
			\hline
			Host galaxy	& Radio source 	& Redshift	& $S_\text{1.4\,GHz}$	& $m_K$ & Dust morphology\\
						& (PKS) 		& 			& (mJy) 			& (mag)	&\\
			\hline 
			ESO 443-G024 & 1258-321 	& 0.01703	& $1387 \pm 45$		& 8.51 & no dust\tnote{a}	\\ 
			IC 1459 	& 2254-367 		& 0.00565 	& $1280 \pm 45$		& 6.81 & dust lane\tnote{b}	\\
			IC 1531 	& 0007-325 		& 0.02553 	& \leavevmode\phantom{0}$388 \pm 12$		& 9.55 & --					\\
			IC 4296		& 1333-\leavevmode\phantom{0}33 		& 0.01248 	& $1342 \pm 41$		& 7.50 & edge-on disc\tnote{b} \\
			NGC 612 	& 0131-\leavevmode\phantom{0}36 		& 0.02954 	& \leavevmode\phantom{0}$585 \pm 18$		& 9.58 & dust lane\tnote{c}	\\
			NGC 1316 	& 0320-\leavevmode\phantom{0}37 & 0.00591 	& \leavevmode\phantom{0}$255 \pm 10$		& 5.59 & dust patches\tnote{b} \\
			NGC 1399 	& 0336-\leavevmode\phantom{0}35 & 0.00472 	& \leavevmode\phantom{0}$209 \pm \leavevmode\phantom{0}7$	& 6.31 & no dust\tnote{b}	\\
			NGC 3100 	& 0958-314 		& 0.00879 	& \leavevmode\phantom{0}$530 \pm 16$		& 8.08 & dust lane\tnote{d}	\\
			NGC 3557 	& 1107-372 		& 0.01016 	& \leavevmode\phantom{0}$484 \pm 16$		& 7.20 & face-on disc\tnote{b}\\
			NGC 7075 	& 2128-388 		& 0.01819 	& \leavevmode\phantom{0}$837 \pm 28$		& 9.56 & --					\\
			--			& 0718-\leavevmode\phantom{0}34 		& 0.02897 	& $1119 \pm 41$		& 9.97 & dust patches\tnote{e} \\
			\hline
			\hline
		\end{tabular}
	% 	\begin{tablenotes}
	% 	\footnotesize
	% 	\note Col.\,1: host galaxy name. Col.\,2: radio source name from Parkes Southern Radio Source Catalogue. Col.\,3: redshift. Col.\,4: National Radio Astronomy Observatory (NRAO) Very Large Array (VLA) Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}. Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}). Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}. 
	% 	\item We hereafter refer to the last galaxy by its PKS name only.
	% 	\end{tablenotes}
	% \end{threeparttable}
	\end{table*}

@@

\section{Observing strategy and Data Reduction}
	\label{sec:obs}
	The sample was observed with VIMOS, mounted on the VLT in Paranal \citep{LeFevre2003}. All observations were taken with a spatial sampling of $0\farcs67$, using the high-resolution blue grism yielding a wavelength range of 3700-5520\,\AA\ with a spectral resolution of 1440 and sampling of 0.71\,\AA\,$\mathrm{pix^{-1}}$. Each object was observed with a total integration time of $\approx 100$\,min on-source, equally spread over three observing blocks (OBs). Each OB also contained all the necessary observation for standard IFS data reduction.

@@

\section{Data Analysis}
	\label{sec:analysis}
	Both VIMOS and MUSE datasets are spatially binned using Voronoi binning\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/} \citep{Cappellari2003} and from this point on are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N). For our purposes, we define the `signal' and `noise' of each spaxel as the median value of its spectrum and noise spectrum, respectively. We require a S/N of 30 for all VIMOS datacubes and 50 for the IC 1459 and IC 4296 MUSE datacubes. The NGC 1316 and NGC 1399 MUSE datacubes were binned to a S/N of 50 for the analysis of the stellar kinematics and 100 for the analysis of the emission line kinematics and stellar populations.

	Next we implement a routine to find optimal initial values of the redshift and velocity dispersion for each galaxy, to be used when fitting individual bins, by means of iterative fits to the spatially collapsed (i.e. summed across both spatial dimensions of the datacube) spectrum. We use the penalized-fitting (\textsc{pPXF}) routine\footnotemark[1] of \citet{Cappellari2004} and \citet{Cappellari2016a} with the Medium-resolution Issac Newton Telescope (INT) Library of Empirical Spectra (MILES) library \citep{Sanchez-Blazquez2006, Falcon-Barroso2011a} to find the best-fitting line-of-sight velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion). The final mean velocity of a given galaxy, is used as its precise spectroscopic redshift and is given in Table \ref{tab:sample}. Beyond this point, each bin is analysed independently.

	\subsection{Stellar Kinematics}
		\label{subsec:starKin}
		Each bin is fit independently, again using \textsc{pPXF} with the MILES library. For the fit, regions around potential emission lines (listed in Section \ref{subsec:EmissionLines}) are masked, and a fourth order polynomial additive continuum correction is used. A Monte--Carlo (MC) estimate of the uncertainties is used.

	\subsection{Ionized Gas Distribution and Kinematics}
		\label{subsec:EmissionLines}
		In this analysis we consider the following emission lines and doublets: [\ion{O}{ii}]$\lambda\lambda$3726,3729, H$\delta$, H$\gamma$, H$\beta$, [\ion{O}{iii}]$\lambda\lambda$4969,5007, [\ion{N}{I}]$\lambda\lambda$5199,5202, [\ion{O}{i}]$\lambda\lambda$6300,6363, [\ion{N}{ii}]$\lambda\lambda$6548,6583, H$\alpha$ and [\ion{S}{ii}]$\lambda\lambda$6716,6731. We fit the fluxes and kinematics for the emission lines using Gaussian templates, independently fitting the emission lines of the ISM, with a single LOSVDs (again parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion), from the stellar kinematics. In the cases of the [\ion{O}{iii}], [\ion{O}{i}] and [\ion{N}{ii}] doublets, the two components of the doublets are fit with a fixed flux ratio of 3:1. The [\ion{N}{i}] doublet has a fixed ratio of 3:2 \citep{Safier1992}. The two components of the [\ion{O}{ii}] and [\ion{S}{ii}] doublets are fit independently. To minimize template mismatch, whereby emission lines are erroneously fitted to the edges of badly modeled and thus subtracted absorption features, we follow the method set out in \citet{Sarzi2005}. In this method the stellar component is first fitted as above with masked potential emission line regions, followed by the unmasking and fitting of the [\ion{O}{iii}] doublet which sets the kinematics for all the emission lines and finally the amplitude of the remaining emission lines is fitted.

@@

		\subsubsection{Correcting for Stellar Velocity Dispersion}
			\label{subsubsec:EmissionFit}
			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption is outside of the central bandpasses. To do this, we create a stellar best-fitting spectrum which is \textit{not} convolved with the best-fitting LOSVD. A given index, $I$, is then measured for both this `unconvolved' spectrum ($I^\text{unc}$) and the convolved best-fitting spectrum ($I^\text{conv}$), and the ratio of these two indices is used as a multiplicative correction factor for the index measured ($I^\text{obs}$), such that the corrected index ($I^\text{corr}$) is given by
			\begin{equation}
				I^\text{corr} \equiv \frac{I^\text{unc}}{I^\text{conv}} I^\text{obs} \, .
			\end{equation}
			These corrected indices are those reported and discussed in the sections below.

	\subsubsection{Best-fitting Stellar Populations}
		\label{subsubsec:stellarPop}
		In each bin, using the measured absorption line strengths, we identify the best-fitting single stellar population (SSP) model from the models of \citeauthor{Thomas2010} (\citeyear{Thomas2010}; hereafter \citetalias{Thomas2010}) using \textsc{emcee}, a \textsc{python}, affine-invariant Markov chain Monte--Carlo (MCMC) fitting package \citep{Foreman-Mackey2013}. The \citetalias{Thomas2010} models are chosen because they are based on high-resolution, flux-calibrated spectra and therefore not requiring absorption line strength measurement to be in the Lick/IDS system.

@@

			In reality, the field of view does not always contain 1 $R_\text{e}$. Where this is the case, we follow the method by \citet{Emsellem2007}, where $R_\text{m}$ is redefined as $R_\text{m} \equiv \sqrt{A_\text{s}/\pi}$, where $A_\text{s}$ is the area of the ellipse contained within the field of view. For a given galaxy, we fit ellipses as described above, up to $R_\text{m} = R_\text{max}$, where $A_\text{s}$ reaches a maximum difference if 15\% to the area of the fitted ellipse, $A_\text{ellipse}$. The value $\epsilon_\text{e}$, the ellipticity at 1 $R_\text{e}$ or $R_\text{max}$, whichever is smallest, is given in Col.\,3 of Table \ref{tab:classify}.

@@

\section{Stellar Kinematics}
	\label{sec:StarKine}
	Using the methods above, we produce stellar kinematic maps for all datacubes (shown in Section \ref{sec:Maps}). Here, we use these maps to classify each galaxy according to the Atlas$^\text{3D}$ regular/non-regular rotator and fast/slow rotator classification schemes of \citet{Krajnovic2006} and \citet{Cappellari2016}, respectively, as well as the qualitative kinematic classes of \citet{Krajnovic2011}. We use the criteria described in the referenced literature for each of these classification, with the results shown in Table \ref{tab:classify}.

	\begin{table*}
		\centering
	% \begin{threeparttable}
		\caption{Kinematic classifications of the Southern Sample galaxies. Col.\,1: Galaxy name. Col.\,2: $\lambda_\text{R}$ evaluated at $R_\text{e}$. Col.\,3: Ellipticity at $R_\text{e}$. Col.\,4: Misalignment angle between the kinematic and photometric position angles. Col.\,5: Fast-/slow-rotator (FR/SR) classification. Col.\,6: Regular-rotator (RR) or non-regular-rotator (NRR). Col.\,7: Kinematic features: kinematically-decoupled core (KDC) or low-velocity (LV). Col.\,8: Kinematic group.}
		\label{tab:classify}
		\begin{tabular}{l c c c c c c c}
			\hline
			\hline
			Galaxy		& $\lambda_\mathrm{R_e}$ & $\epsilon_\text{e}$  & $\Gamma_\text{kin}$ & FR/SR 	& RR/NRR 	& Feature & Group 	\\
			 & & & (deg) \\
			\hline 
			ESO 443-G024 & 0.048 & 0.35 & $-18\pm\leavevmode\phantom{0}2$	& SR & NRR & KDC & c \\
			IC 1459 	& 0.125 & 0.24 & \leavevmode\phantom{0}$-3\pm\leavevmode\phantom{0}1$ & SR & NRR & KDC & c \\
			IC 1531 	& 0.101 & 0.08 & $-54\pm25$	& FR & NRR & LV & a \\
			IC 4296		& 0.034 & 0.03 & \leavevmode\phantom{$-0$}$8\pm12$ & SR &\leavevmode\phantom{N}RR & -- & e \\
			NGC 612 	& 0.655 & 0.36 & \leavevmode\phantom{$-$}$12\pm\leavevmode\phantom{0}6$	& FR &\leavevmode\phantom{N}RR & -- & e \\
			NGC 1316 	& 0.100 & 0.39 & \leavevmode\phantom{$-0$}$6\pm\leavevmode\phantom{0}2$ & FR & NRR & -- & f \\
			NGC 1399 	& 0.090 & 0.12 & $-74\pm\leavevmode\phantom{0}5$ & SR & NRR & LV & a \\
			NGC 3100 	& 0.354 & 0.24 & \leavevmode\phantom{0}$-8\pm\leavevmode\phantom{0}2$ & FR &\leavevmode\phantom{N}RR & -- & e \\
			NGC 3557 	& 0.312 & 0.20 & \leavevmode\phantom{$-$}$16\pm\leavevmode\phantom{0}5$ & FR &\leavevmode\phantom{N}RR & -- & e\\
			NGC 7075 	& 0.068 & 0.04 & \leavevmode\phantom{$-$}$36\pm50$ & SR & NRR & -- & b \\
			PKS 718-34  & 0.159 & 0.17 & \leavevmode\phantom{$-$}$15\pm25$ & FR & NRR & KDC\tnote{a} & b\\
			\hline
			\hline
			\multicolumn{8}{L{.7\linewidth}}{$^{a}$Tentative classification. A higher S/N in the outer regions of the field of view is required for confirmation.}

@@

	\subsection{Regular/Non-regular Rotators}
		\label{subsec:RR}
		We find 4/11, or $(36\pm15)$\%, of our sample galaxies are regular rotators. This compares to 82\% of the Atlas$^\text{3D}$ sample being classified as regular rotators \citep{Krajnovic2011}. However the likely-hood of a given galaxy being a regular rotator is highly mass dependent with the likely-hood decreasing with increasing mass. Thus since our Southern sample are all extremely massive galaxies, we expect to find a higher fraction of non-regular rotators than the Atlas$^\text{3D}$ survey.

@@

\section{Absorption Line Strengths}
	\label{sec:absorption}
	Using the methods described in Section \ref{subsec:absorption} we produce maps of the absorption line strength indices for each galaxy (shown in Appendix \ref{sec:Maps}). Here we measure the Mg\,--\,velocity dispersion relation and compare our absorption line strength measurements to the literature.

@@

		We also observe that the offset in the Fe5015 index is also quite large in comparisons with \citet{Rampazzo2005} and \citet{Vazdekis2010}. In the case of the comparison with \citet{Rampazzo2005} we suggest that the difference is due to differences in method for accounting for the [\ion{O}{iii}] emission lines, however the origin of the offset is less clear in case of the comparison with \citet{Vazdekis2010}.

>>>>

% \usepackage[flushleft, referable]{threeparttablex} % Adding notes under tables
\usepackage[version=4]{mhchem} 	% typeset chemistry symbols
\usepackage{array} % For wrapping text in cell in tables with multicolumntype
% \usepackage{pdflscape} % for landscape pages

% *****************************************************************
% THis is my setting to avoid a particular LaTeX error due to links running
% onto new pages.
\hypersetup{draft}
% *****************************************************************

@@

We present a complete sample of 11 nearby low-powered radio galaxies, observed with a suite of instruments. This paper focuses on the spatially-resolved stellar kinematics, stellar populations, and ionized gas distribution, kinematics and ionization derived from optical IFS observations%, while other observation such as \ce{^{12}CO(2-1)} from Atacama Large Millimetre/sub-millimetre Array (ALMA) and radio continuum from the Very Large Array (VLA) will be presented in future papers
. We compare the characteristics and properties of our sample to those of ordinary (i.e.\ optically-selected) ETGs using the Atlas$^\text{3D}$ and MASSIVE IFS surveys. These include the fast/slow rotator classification fraction, kinematic substructures, absorption line strength radial gradients, general stellar population properties, ionized gas distribution and kinematics and the dominant source of ionizing photons.

@@

\section{Introduction}
	\label{sec:intro}
	It is becoming increasingly clear that active galactic nuclei (AGN) can be separated into two different types, radiative and jet mode AGN \citep[e.g.][]{Antonucci2012, Heckman2014}, raising speculation about differing mechanisms and possibly fuel sources for each. The former is thought to be the powerful engine that initially and rapidly shuts off star formation in massive early-type galaxies (ETGs; e.g. \citealt{Thomas2005, Thomas2010}), either by removing the cold gas from the galaxy entirely, heating it such that it joins the hot X-ray gas often present in massive galaxies \citep[e.g.][]{OSullivan2001}, or rendering it unusable for star formation (such as by stabilising it against collapse; e.g.\ \citealt{Martig2009}). After a single radiative-mode episode, the AGN is thought to subside to become jet-dominated, repeatedly reheating the surrounding interstellar medium (ISM) to counter any cooling that might allow the cold gas reservoir to replenish (and subsequently form stars).

@@

	\begin{table*}
		\centering
	% \begin{threeparttable}
		\caption{Key characteristics of the Southern Sample galaxies. Col.\,1: host galaxy name. Col.\,2: radio source name from Parkes Southern Radio Source Catalogue. We hereafter refer to the last galaxy by its PKS name only. Col.\,3: redshift. Col.\,4: National Radio Astronomy Observatory (NRAO) VLA Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}. Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}). Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}.}
		\label{tab:sample}
		\begin{tabular}{l c c c c l}
			\hline
			\hline
			Host galaxy	& Radio source 	& Redshift	& $S_\text{1.4\,GHz}$	& $m_K$ & Dust morphology\\
						& (PKS) 		& 			& (mJy) 			& (mag)	&\\
			\hline 
			ESO 443-G024 & 1258-321 	& 0.01703	& $1387 \pm 45$		& 8.51 & no dust$^{a}$	\\ 
			IC 1459 	& 2254-367 		& 0.00565 	& $1280 \pm 45$		& 6.81 & dust lane$^{b}$	\\
			IC 1531 	& 0007-325 		& 0.02553 	& \leavevmode\phantom{0}$388 \pm 12$		& 9.55 & --					\\
			IC 4296		& 1333-\leavevmode\phantom{0}33 		& 0.01248 	& $1342 \pm 41$		& 7.50 & edge-on disc$^{b}$ \\
			NGC 612 	& 0131-\leavevmode\phantom{0}36 		& 0.02954 	& \leavevmode\phantom{0}$585 \pm 18$		& 9.58 & dust lane$^{c}$	\\
			NGC 1316 	& 0320-\leavevmode\phantom{0}37 & 0.00591 	& \leavevmode\phantom{0}$255 \pm 10$		& 5.59 & dust patches$^{b}$ \\
			NGC 1399 	& 0336-\leavevmode\phantom{0}35 & 0.00472 	& \leavevmode\phantom{0}$209 \pm \leavevmode\phantom{0}7$	& 6.31 & no dust$^{b}$	\\
			NGC 3100 	& 0958-314 		& 0.00879 	& \leavevmode\phantom{0}$530 \pm 16$		& 8.08 & dust lane$^{d}$	\\
			NGC 3557 	& 1107-372 		& 0.01016 	& \leavevmode\phantom{0}$484 \pm 16$		& 7.20 & face-on disc$^{b}$\\
			NGC 7075 	& 2128-388 		& 0.01819 	& \leavevmode\phantom{0}$837 \pm 28$		& 9.56 & --					\\
			--			& 0718-\leavevmode\phantom{0}34 		& 0.02897 	& $1119 \pm 41$		& 9.97 & dust patches$^{e}$ \\
			\hline
			\hline
		\end{tabular}
	% 	\begin{tablenotes}
	% 	\footnotesize
	% 	\note Col.\,1: host galaxy name. Col.\,2: radio source name from Parkes Southern Radio Source Catalogue. Col.\,3: redshift. Col.\,4: National Radio Astronomy Observatory (NRAO) Very Large Array (VLA) Sky Survey (NVSS) 1.4 GHz flux density \citep{Condon1998}. Col.\,5: Two Micron All Sky Survey (2MASS) $K$-band apparent magnitude (with errors of $\pm 0.025$ mag; \citealt{Skrutskie2006}). Col.\,6: dust morphologies from (a) \citet{Govoni2000}, (b) \citet{Lauer2005}, (c) \citet{Bettoni2001}, (d) \citet{Sandage1979}, (e) \citet{Colbert2001}. 
	% 	\item We hereafter refer to the last galaxy by its PKS name only.
	% 	\end{tablenotes}
	% \end{threeparttable}
	\end{table*}

@@

\section{Observing strategy and Data Reduction}
	\label{sec:obs}
	The sample has been observed with a suit of instruments spanning the radio to optical wavelengths (archival images from the \textit{Chandra space telescope} are also available for some of the sample). This paper focuses on the optical IFS observations made with VIMOS, mounted on the VLT in Paranal \citep{LeFevre2003}. All observations were taken with a spatial sampling of $0\farcs67$, using the high-resolution blue grism yielding a wavelength range of 3700-5520\,\AA\ with a spectral resolution of 1440 and sampling of 0.71\,\AA\,$\mathrm{pix^{-1}}$. Each object was observed with a total integration time of $\approx 100$\,min on-source, equally spread over three observing blocks (OBs). Each OB also contained all the necessary observation for standard IFS data reduction.

@@

\section{Data Analysis}
	\label{sec:analysis}
	Both VIMOS and MUSE datasets are spatially binned using Voronoi binning\footnote{http://www-astro.physics.ox.ac.uk/~mxc/software/} \citep{Cappellari2003} and from this point on are treated almost identically, the only difference (other than the different spectral ranges and resolutions) being that the MUSE datacubes are spatially binned to a higher signal-to-noise ratio (S/N). For our purposes, we define the `signal' and `noise' of each spaxel as the median value of its spectrum and noise spectrum, respectively. We require a S/N of 30 for all VIMOS datacubes and 50 for the IC 1459 and IC 4296 MUSE datacubes. The NGC 1316 and NGC 1399 MUSE datacubes were binned to a S/N of 50 for the analysis of the stellar kinematics and 100 for the analysis of the emission line kinematics and stellar populations.

	Next we implement a routine to find optimal initial values of the redshift and velocity dispersion for each galaxy, to be used when fitting individual bins, by means of iterative fits to the spatially collapsed (i.e. summed across both spatial dimensions of the datacube) spectrum. We use the penalized-fitting (\textsc{pPXF}) routine\footnotemark[1] of \citet{Cappellari2004} and \citet{Cappellari2016a} with the Medium-resolution Isaac Newton Telescope (INT) Library of Empirical Spectra (MILES) library \citep{Sanchez-Blazquez2006, Falcon-Barroso2011a} to find the best-fitting line-of-sight stellar velocity distribution (LOSVD; as parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion). The final mean velocity of a given galaxy, is used as its precise spectroscopic redshift and is given in Table \ref{tab:sample}. Beyond this point, each bin is analysed independently.

	It was noted that for the MUSE observations of NGC 1316, the NaD absorption feature (which as generally attributed to absorption from the ISM and is thus affected by the kinematics of the ISM) was significantly effecting the quality of the stellar best-fitting spectrum. For this reason, the wavelength range of NGC 1316 spectra was limited to $<5800 \, \AA$ whilst fitting for the stellar spectra only.

	\subsection{Stellar Kinematics}
		\label{subsec:starKin}
		Each bin is fit independently, again using \textsc{pPXF} with the MILES library. For the fit, regions around potential emission lines (listed in Section \ref{subsec:EmissionLines}) are masked, and a fourth order polynomial additive continuum correction is used. The residuals between the best-fitting spectrum and the input spectrum are smoothed in wavelength using a weighted, moving average. This is then summed in quadrature with the noise spectrum (as propagated through the data reduction pipeline) to produce a combined `residual noise' spectrum. A Monte--Carlo (MC) method is used to propagate this residual noise to give to give the quoted uncertainties.

	\subsection{Ionized Gas Distribution and Kinematics}
		\label{subsec:EmissionLines}
		In this analysis we consider the following emission lines and doublets: H$\gamma$, H$\beta$, [\ion{O}{iii}]$\lambda\lambda$4969,5007, [\ion{N}{I}]$\lambda\lambda$5199,5202, [\ion{O}{i}]$\lambda\lambda$6300,6363, [\ion{N}{ii}]$\lambda\lambda$6548,6583, H$\alpha$ and [\ion{S}{ii}]$\lambda\lambda$6716,6731. We fit the fluxes and kinematics for the emission lines using Gaussian templates, independently fitting the emission lines of the ISM, with a single LOSVDs (again parametrised by the Gaussian parameters $v$, the mean velocity and $\sigma$, the velocity dispersion), from the stellar kinematics. In the cases of the [\ion{O}{iii}], [\ion{O}{i}] and [\ion{N}{ii}] doublets, the two components of the doublets are fit with a fixed flux ratio of 3:1. The [\ion{N}{i}] doublet has a fixed ratio of 3:2 \citep{Safier1992}. The two components of the [\ion{O}{ii}] and [\ion{S}{ii}] doublets are fit independently. To minimize template mismatch, whereby emission lines are erroneously fitted to the edges of badly modelled and thus subtracted absorption features, we follow the method set out in \citet{Sarzi2005}. In this method the stellar component is first fitted as above with masked potential emission line regions, followed by the unmasking and fitting of the [\ion{O}{iii}] doublet which sets the kinematics for all the emission lines and finally the amplitude of the remaining emission lines is fitted.

@@

		\subsubsection{Correcting for Stellar Velocity Dispersion}
			\label{subsubsec:EmissionFit}
			We correct for the effect of the different velocity dispersions of the stars which varyingly spread absorption features such that differing fractions of the absorption are outside of the central bandpasses. To do this, we create a stellar best-fitting spectrum which is \textit{not} convolved with the best-fitting LOSVD. Note that for NGC 1316, indices at wavelengths longer than 5800 \AA\ are calculated using the extrapolated best-fitting \textit{pPXF} fit. A given index, $I$, is then measured for both this `unconvolved' spectrum ($I^\text{unc}$) and the convolved best-fitting spectrum ($I^\text{conv}$), and the ratio of these two indices is used as a multiplicative correction factor for the index measured ($I^\text{obs}$), such that the corrected index ($I^\text{corr}$) is given by
			\begin{equation}
				I^\text{corr} \equiv \frac{I^\text{unc}}{I^\text{conv}} I^\text{obs} \, .
			\end{equation}
			These corrected indices are those reported and discussed in the sections below.

	\subsubsection{Best-fitting Stellar Populations}
		\label{subsubsec:stellarPop}
		In each bin, using the measured absorption line strengths, we identify the best-fitting single stellar population (SSP) model from an interpolated grid of models using \textsc{emcee}, a \textsc{python}, affine-invariant Markov chain Monte--Carlo (MCMC) fitting package \citep{Foreman-Mackey2013}. This grid is created by linearly interpolating between the models of \citeauthor{Thomas2010} (\citeyear{Thomas2010}; hereafter \citetalias{Thomas2010}). The \citetalias{Thomas2010} models are chosen because they are based on high-resolution, flux-calibrated spectra and therefore not requiring absorption line strength measurement to be in the Lick/IDS system.

@@

			In reality, the field of view does not always contain 1 $R_\text{e}$. Where this is the case, we follow the method by \citet{Emsellem2007}, where $R_\text{m}$ is redefined as $R_\text{m} \equiv \sqrt{A_\text{s}/\pi}$, where $A_\text{s}$ is the area of the ellipse contained within the field of view. For a given galaxy, we fit ellipses as described above, up to $R_\text{m} = R_\text{max}$, where $A_\text{s}$ reaches a maximum difference of 15\% to the area of the fitted ellipse, $A_\text{ellipse}$. The value $\epsilon_\text{e}$, the ellipticity at 1 $R_\text{e}$ or $R_\text{max}$, whichever is smallest, is given in Col.\,3 of Table \ref{tab:classify}.

@@

\section{Stellar Kinematics}
	\label{sec:StarKine}
	Using the methods above, we produce stellar kinematic maps for all datacubes (shown in Section \ref{sec:maps}). Here, we use these maps to classify each galaxy according to the Atlas$^\text{3D}$ regular/non-regular rotator and fast/slow rotator classification schemes of \citet{Krajnovic2006} and \citet{Cappellari2016}, respectively, as well as the qualitative kinematic classes of \citet{Krajnovic2011}. We use the criteria described in the referenced literature for each of these classification, with the results shown in Table \ref{tab:classify}.

	\begin{table*}
		\centering
	% \begin{threeparttable}
		\caption{Kinematic classifications of the Southern Sample galaxies. Col.\,1: Galaxy name. Col.\,2: $\lambda_\text{R}$ evaluated at $R_\text{e}$. Col.\,3: Ellipticity at $R_\text{e}$. Col.\,4: Misalignment angle between the kinematic and photometric position angles. Col.\,5: Fast-/slow-rotator (FR/SR) classification. Col.\,6: Regular-rotator (RR) or non-regular-rotator (NRR). Col.\,7: Kinematic features: kinematically-decoupled core (KDC) or low-velocity (LV). Col.\,8: Kinematic group.}
		\label{tab:classify}
		\begin{tabular}{l c c c c c c c}
			\hline
			\hline
			Galaxy		& $\lambda_\mathrm{R_e}$ & $\epsilon_\text{e}$  & $\Gamma_\text{kin}$ & FR/SR 	& RR/NRR 	& Feature & Group 	\\
			 & & & (deg) \\
			\hline 
			ESO 443-G024 & 0.048 & 0.35 & $-18\pm\leavevmode\phantom{0}2$	& SR & NRR & KDC & c \\
			IC 1459 	& 0.125 & 0.24 & \leavevmode\phantom{0}$-3\pm\leavevmode\phantom{0}1$ & SR & NRR & KDC & c \\
			IC 1531 	& 0.101 & 0.08 & $-54\pm25$	& FR & NRR & LV & a \\
			IC 4296		& 0.034 & 0.03 & \leavevmode\phantom{$-0$}$8\pm12$ & SR &\leavevmode\phantom{N}RR & -- & e \\
			NGC 612 	& 0.655 & 0.36 & \leavevmode\phantom{$-$}$12\pm\leavevmode\phantom{0}6$	& FR &\leavevmode\phantom{N}RR & -- & e \\
			NGC 1316 	& 0.100 & 0.39 & \leavevmode\phantom{$-0$}$6\pm\leavevmode\phantom{0}2$ & FR & NRR & -- & f \\
			NGC 1399 	& 0.090 & 0.12 & $-74\pm\leavevmode\phantom{0}5$ & SR & NRR & LV & a \\
			NGC 3100 	& 0.354 & 0.24 & \leavevmode\phantom{0}$-8\pm\leavevmode\phantom{0}2$ & FR &\leavevmode\phantom{N}RR & -- & e \\
			NGC 3557 	& 0.312 & 0.20 & \leavevmode\phantom{$-$}$16\pm\leavevmode\phantom{0}5$ & FR &\leavevmode\phantom{N}RR & -- & e\\
			NGC 7075 	& 0.068 & 0.04 & \leavevmode\phantom{$-$}$36\pm50$ & SR & NRR & -- & b \\
			PKS 718-34  & 0.159 & 0.17 & \leavevmode\phantom{$-$}$15\pm25$ & FR & NRR & KDC$^{a}$ & b\\
			\hline
			\hline
			\multicolumn{8}{L{.7\linewidth}}{$^{a}$Tentative classification. A higher S/N in the outer regions of the field of view is required for confirmation.}

@@

	\subsection{Regular/Non-regular Rotators}
		\label{subsec:RR}
		We find 4/11, or $(36\pm15)$\%, of our sample galaxies are regular rotators. This compares to 82\% of the Atlas$^\text{3D}$ sample being classified as regular rotators \citep{Krajnovic2011}. However the likelihood of a given galaxy being a regular rotator is highly mass dependent with the likelihood decreasing with increasing mass. Thus since our Southern sample are all extremely massive galaxies, we expect to find a higher fraction of non-regular rotators than the Atlas$^\text{3D}$ survey.

@@

\section{Absorption Line Strengths}
	\label{sec:absorption}
	Using the methods described in Section \ref{subsec:absorption} we produce maps of the absorption line strength indices for each galaxy (shown in Appendix \ref{sec:maps}). Here we measure the Mg\,--\,velocity dispersion relation and compare our absorption line strength measurements to the literature.

@@

		We also observe that the offset in the Fe5015 index is also quite large in comparisons with \citet{Rampazzo2005} and \citet{Vazdekis2010}. In the case of the comparison with \citet{Rampazzo2005} we suggest that the difference is due to differences in method for accounting for the [\ion{O}{iii}] emission doublet, however the origin of the offset is less clear in case of the comparison with \citet{Vazdekis2010}.
